%-------------------------
% Resume in Latex
% Author : Manoel L. Carvalho
% Base CV — Full Version
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Manoel L. Carvalho} \\ \vspace{2pt}
  \small \textbf{Full Stack Engineer \& Technical Lead | Backend-Focused | Cloud-Native | Fintech \& Healthcare} \\ \vspace{4pt}
  \small
  +55 (81) 98182-9698 $|$
  \href{mailto:mlc6dev@gmail.com}{\underline{mlc6dev@gmail.com}} $|$
  \href{https://www.linkedin.com/in/manoel-carvalho-350507236/}{\underline{linkedin.com/in/manoel-carvalho}} $|$
  \href{https://github.com/Mlcarvalho1}{\underline{github.com/Mlcarvalho1}} $|$
  Recife, Brazil
\end{center}

%-----------PROFILE-----------
\section{Profile}
\small{
Full Stack Engineer and Technical Lead with 4+ years of experience designing, building, and shipping complex production platforms from the ground up. Core developer and current lead of \textbf{Amigo One} — a comprehensive healthcare and fintech ecosystem serving \textbf{25,000 monthly active users (10,000 daily)} across web and mobile — encompassing AI-assisted medical consultations (Google Gemini), digital banking with BACEN compliance (AmigoPay via Dock BaaS), medical records, patient management, scheduling, a medical social network, and financial management modules.

Deep expertise across the full stack: Node.js/NestJS backend architectures, React/Next.js web applications, React Native mobile apps (App Store + Google Play), PostgreSQL and MongoDB data modeling, and CI/CD infrastructure with Docker and GitHub Actions. Experienced leading cross-functional teams, mentoring engineers, collaborating directly with founders and stakeholders, and making pragmatic technical trade-offs in fast-moving, cost-conscious environments. Comfortable in async, remote-first settings with a high degree of ownership and autonomy.
}

%-----------EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

  %--- Amigo Tech: Team Lead ---
  \resumeSubheading
    {Amigo Tech}{Recife, Brazil}
    {Development Team Lead}{Feb 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Lead all engineering decisions for the Amigo One platform, managing feature roadmap execution, technical architecture, and team delivery across web, mobile, and backend systems.}
    \resumeItem{Drive the evolution of Amigo One's AI capabilities, overseeing the Google Gemini integration for real-time clinical consultation assistance, and evaluating new AI tooling to embed across the platform.}
    \resumeItem{Define and enforce code quality standards, review processes, and shared engineering practices across the team; mentor junior and mid-level engineers through pairing, code reviews, and technical guidance.}
    \resumeItem{Collaborate directly with founders, product managers, and non-technical stakeholders to translate business requirements into technical specifications and delivery plans.}
    \resumeItem{Oversee infrastructure decisions including CI/CD pipeline improvements (GitHub Actions), containerization strategy (Docker), and cloud deployment practices on AWS and Vercel.}
    \resumeItem{Lead hiring and onboarding processes for new engineering team members, ensuring alignment with technical standards and team culture.}
  \resumeItemListEnd

  %--- Amigo Tech: Software Engineer ---
  \resumeSubheading
    {}{}
    {Software Engineer}{Jan 2023 -- Feb 2025}
  \resumeItemListStart
    \resumeItem{Core developer of \textbf{Amigo One}, contributing to the majority of its modules from inception: AmigoPay (digital banking), AI consultation assistant, patient management, medical social feed, finances management, and onboarding/activation flows.}
    \resumeItem{Built and maintained the \textbf{Node.js/NestJS} backend microservice architecture powering Amigo One, including RESTful API design, complex clinical and financial business logic, authentication/authorization flows, and third-party service integrations.}
    \resumeItem{Developed the \textbf{React Native} mobile application for Amigo One (iOS + Android), including core banking screens, AI consultation UI, patient dashboards, and financial transaction flows — shipped to both the \textbf{Apple App Store} and \textbf{Google Play Store}.}
    \resumeItem{Built the \textbf{React/Next.js} web platform, delivering responsive, data-rich interfaces including clinical dashboards, historical trend visualizations, medical social feed, and administrative modules.}

    % AmigoPay
    \resumeItem{\textbf{AmigoPay — Digital Banking Module:} Integrated \textbf{Dock (formerly Conductor)} BaaS platform to deliver a fully BACEN-compliant digital bank within the app, covering: PIX (send/receive), TED transfers, Boleto generation and payment, account balance and statements, bank limit management, password management, and deep integration with the Amigo internal finance system.}

    % AI
    \resumeItem{\textbf{AI Consultation Assistant:} Built the end-to-end \textbf{Google Gemini} integration for real-time AI-assisted medical consultations — including API integration layer, prompt architecture, product specification co-authorship, and React Native/React frontend delivery.}

    % Mobile quality
    \resumeItem{Implemented \textbf{Firebase Crashlytics} and \textbf{Sentry} for real-time crash reporting and production monitoring across iOS and Android, maintaining high crash-free session rates; set up \textbf{Firebase Analytics} for funnel tracking and feature adoption analysis.}

    % State management
    \resumeItem{Implemented mobile state management using \textbf{Redux} and \textbf{Context API} across complex multi-step financial and clinical flows; applied \textbf{TanStack Query} for server state management and data synchronization on web surfaces.}

    % DB
    \resumeItem{Designed and optimized \textbf{PostgreSQL} schemas for clinical and financial data models, applying indexing strategies, query optimization, and relational modeling for production scale; worked with \textbf{MongoDB} via Mongoose and Prisma for document-oriented service data.}

    % Infra
    \resumeItem{Built and maintained \textbf{CI/CD pipelines} with GitHub Actions and containerized services with Docker, enabling reliable multi-environment deployments and production stability across web and mobile release tracks.}
  \resumeItemListEnd

  %--- Japox ---
  \resumeSubheading
    {Japox Co.}{Tokyo, Japan (on site)}
    {Global Software Engineering Intern}{Oct 2025 -- Dec 2025}
  \resumeItemListStart
    \resumeItem{Built and scaled \textbf{Golang} backend gateway services with a focus on authentication, authorization, API key lifecycle management, rate limiting, and high-throughput performance — achieving sub-100ms response latency under production load.}
    \resumeItem{Developed secure token-based access control systems and API key management for production clients serving real traffic.}
    \resumeItem{Delivered \textbf{React} dashboards for real-time monitoring of usage analytics and platform performance metrics.}
    \resumeItem{Collaborated asynchronously across time zones in a fully remote, internationally distributed team — shipping features rapidly in a startup-style environment with direct exposure to founders and senior engineers.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  %--- Amigo One ---
  \resumeProjectHeading
    {\textbf{Amigo One} $|$ \emph{Full-Scale Healthcare \& Fintech Platform} $|$ \emph{25,000 MAU / 10,000 DAU}}{2023 -- Present}
  \resumeItemListStart
    \resumeItem{End-to-end development and technical leadership of a multi-module platform serving 25,000 monthly active users (10,000 daily) across \textbf{web (React, Next.js)} and \textbf{mobile (React Native, iOS + Android)}.}
    \resumeItem{\textbf{Modules built:} AI consultation assistant (Google Gemini), AmigoPay digital banking (Dock BaaS), patient management, medical records, appointment scheduling, medical social feed, and financial management.}
    \resumeItem{\textbf{Backend:} Node.js, NestJS, TypeScript, PostgreSQL, MongoDB, Redis, Prisma, Mongoose, REST APIs, microservice architecture.}
    \resumeItem{\textbf{Mobile:} React Native, Redux, Context API, Firebase Crashlytics, Firebase Analytics, Sentry, App Store + Google Play deployment and lifecycle management.}
    \resumeItem{\textbf{Web:} React, Next.js, TanStack Query, React Hook Form, Vite — including complex data dashboards, real-time views, and administrative interfaces.}
    \resumeItem{\textbf{Infrastructure:} Docker, GitHub Actions CI/CD, AWS, Vercel — supporting multiple daily deployments across web and mobile release pipelines.}
  \resumeItemListEnd

  %--- AmigoPay ---
  \resumeProjectHeading
    {\textbf{AmigoPay} $|$ \emph{BACEN-Compliant Digital Banking Module} $|$ \emph{Dock BaaS Integration}}{2023 -- Present}
  \resumeItemListStart
    \resumeItem{Built a fully regulated Brazilian digital banking experience within Amigo One, meeting all BACEN requirements for a licensed bank application.}
    \resumeItem{Integrated Dock (formerly Conductor) BaaS to deliver: PIX (send/receive), TED, Boleto generation and payment, account balance/statements, bank limits, password management, and integration with Amigo's internal finance system.}
    \resumeItem{Owned the full transaction flow across mobile (React Native) and backend (Node.js/NestJS + PostgreSQL), from user-facing UI to secure financial data handling.}
  \resumeItemListEnd

  %--- ShunCar ---
  \resumeProjectHeading
    {\textbf{ShuunCar Platform} $|$ \emph{Vehicle Data Intelligence Platform} $|$ \emph{Production}}{2025}
  \resumeItemListStart
    \resumeItem{Built a full stack web platform for VIN-based vehicle data analysis, owning frontend (React, TanStack Query), REST API backend (Node.js), and cloud deployment (Vercel, Supabase).}
    \resumeItem{Integrated MongoDB and Supabase with caching strategies and robust error handling for reliable, performant data delivery under real usage.}
  \resumeItemListEnd

  %--- ShunCar Gateway ---
  \resumeProjectHeading
    {\textbf{ShunCar Gateway} $|$ \emph{Production API Gateway \& Backend Platform}}{Nov 2025 -- Dec 2025}
  \resumeItemListStart
    \resumeItem{Engineered a production-grade backend gateway with modular microservice design: authentication, API key lifecycle management, rate limiting, and secure access control.}
    \resumeItem{Designed cross-database integrations across PostgreSQL and MongoDB using Prisma and Mongoose; implemented caching and observability layers for platform monitoring.}
    \resumeItem{\textbf{Stack:} Node.js, Go, PostgreSQL, MongoDB, Prisma, Mongoose, Supabase.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Languages} \\
\hspace*{1em} TypeScript (Expert), JavaScript (Expert), Go, Python, SQL \\ \vspace{4pt}

\textbf{Backend} \\
\hspace*{1em} Node.js, NestJS, Express, REST APIs, WebSockets, Microservice Architecture \\
\hspace*{1em} PostgreSQL (schema design, query optimization, indexing), MongoDB (Mongoose, Prisma) \\
\hspace*{1em} Supabase, Redis (caching), Authentication \& Authorization (JWT, token-based, role-based access control) \\ \vspace{4pt}

\textbf{Frontend} \\
\hspace*{1em} React.js, Next.js, React Native (iOS + Android) \\
\hspace*{1em} TanStack Query / TanStack Table, React Hook Form, Redux Toolkit, Context API \\
\hspace*{1em} HTML5, CSS3, Vite \\ \vspace{4pt}

\textbf{AI \& Integrations} \\
\hspace*{1em} Google Gemini API (integration, prompt architecture, real-time delivery) \\
\hspace*{1em} Dock BaaS (formerly Conductor) — PIX, TED, Boleto, BACEN-compliant financial flows \\ \vspace{4pt}

\textbf{Mobile} \\
\hspace*{1em} React Native (Expert), iOS + Android deployment, App Store \& Google Play lifecycle \\
\hspace*{1em} Firebase Crashlytics, Firebase Analytics, Sentry — crash reporting, monitoring, funnel analysis \\ \vspace{4pt}

\textbf{Infrastructure \& DevOps} \\
\hspace*{1em} Docker, GitHub Actions (CI/CD), AWS (learning), Vercel, Render \\ \vspace{4pt}

\textbf{Architecture \& Practices} \\
\hspace*{1em} Full Stack Ownership, System Design, API Scalability, Performance Optimization \\
\hspace*{1em} Code Review, Technical Leadership, Cross-functional Collaboration, Async Remote Work \\

}}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Federal University of Pernambuco (UFPE)}{Recife, Brazil}
    {B.Sc. in Computer Engineering}{Expected 2028}
\resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
  \textbf{Portuguese:} Native speaker \\
  \textbf{English:} Advanced — Professional Working Proficiency (reading, writing, speaking)
}}
\end{itemize}

\end{document}